---
title: "Commentary on Replication 2: Extension"
author: "Keeley MacAfee"
date: "2/25/2019"
output: html_document
---


# Abstract
In this commentary, I aim to expand upon Ryan Enos' article "Causal effect of intergroup contact on exclusionary attitudes." Using the data he collected, I examine the magnitude of the change in response to the three survey questions Enos asked regarding opinions on immigration. In this case, I chose to use the magnitude of change to eliminate the inconsistency in measuring the change in response on the 1-5 strongly agree to strongly disagree scale, as the meaning of positive or negative change in response varies between questions. Thus, by examining age, education, and income, I determine which of these factors, if any, affect respondents' malleability in either direction.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ri)
library(RItools)
library(car)
library(xtable)
library(effects)
library(RColorBrewer)
library(gt)
library(kableExtra)
library(rstanarm)
library(tidyverse)
```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load data in. Only need full data set.

raw.data <- read_csv("dataverse_files/pnas_data.csv")

#Elected to use only magnitude of change because the connotations of the questions were different. ex: third question different from the first two; wanted to just look at how much attitudes changed in general rather than distinguishing between exclusionary vs softening attitudes as a result of exposure to outgroups 

x <- raw.data %>%
select(X1, treated_unit, numberim.x, numberim.y, Remain.x, Remain.y, Englishlan.x, Englishlan.y, age, education, income, treatment) %>%
  mutate(number.im.change = numberim.y - numberim.x,
         remain.change = Remain.y - Remain.x,
         english.change = Englishlan.y - Englishlan.x,
         q.full.x = numberim.x + Remain.x + Englishlan.x,
         q.full.y = numberim.y + Remain.y + Englishlan.y,
         q.full.change = q.full.y - q.full.x) %>%
  mutate(mag.change = abs(q.full.change)) %>%
  filter(q.full.change != "NA")

control <- x %>%
  filter(treatment == 0)

treated <- x %>%
  filter(treatment == 1)
```



#Raw Data Regressions
In these three regressions, I use age, education, and income separately to determine if they impacted all of the respondents (control group and treated group).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Age: magnitude
#No significance 
# lm(mag.change ~ age, data = x) %>%
#   summary()

ggplot(x, aes(x = age, y = mag.change)) + geom_smooth(method = "lm") + xlab("Age") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Age: All Respondents")
```

In this case, the intercept has a significant p value (0.002) but age is insignificant (p = 0.56). 



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Education: magnitude
# lm(mag.change ~ education, data = x) %>%
#   summary()

ggplot(x, aes(x = education, y = mag.change)) + geom_smooth(method = "lm") + xlab("Education") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Education: All Respondents")
```

In this case, education is insignificant (p = 0.63).



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Income: magnitude
# lm(mag.change ~ income, data = x) %>%
#   summary()

ggplot(x, aes(x = income, y = mag.change)) + geom_smooth(method = "lm") + xlab("Income") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Income: All Respondents")
```

In this case, income is insignificant (p = 0.51). 


#Control Group Regressions
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Control: age
# lm(mag.change ~ age, data = control) %>%
#   summary()

ggplot(treated, aes(x = age, y = mag.change)) + geom_smooth(method = "lm") + xlab("Age") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Age: Control")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Control: education
# lm(mag.change ~ education, data = control) %>%
#   summary()

ggplot(treated, aes(x = education, y = mag.change)) + geom_smooth(method = "lm") + xlab("Education") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Education: Control")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Control: income
# lm(mag.change ~ income, data = control) %>%
#   summary()

ggplot(treated, aes(x = income, y = mag.change)) + geom_smooth(method = "lm") + xlab("Income") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Income: Control")
```


# Treatment Group Regressions

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Treatment: age
# lm(mag.change ~ age, data = treated) %>%
#   summary()

ggplot(treated, aes(x = age, y = mag.change)) + geom_smooth(method = "lm") + xlab("Age") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Age: Treatment")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Treatment: education
# lm(mag.change ~ education, data = treated) %>%
#   summary()

ggplot(treated, aes(x = education, y = mag.change)) + geom_smooth(method = "lm") + xlab("Education") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Education: Treatment")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Treatment: income
# lm(mag.change ~ income, data = treated) %>%
#   summary()

ggplot(treated, aes(x = income, y = mag.change)) + geom_smooth(method = "lm") + xlab("Income") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Income: Treatment")
```

# Bonus Regression 



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Income: q full (KEEP AS BONUS...SIGNIFICANT)
# lm(q.full.change ~ income, data = x) %>%
#   summary()

ggplot(x, aes(x = income, y = q.full.change)) + geom_smooth(method = "lm") + xlab("Income") + ylab("Change") + ggtitle("Raw Change by Age: All Respondents")
```


