---
title: "Commentary on Replication 2: Extension"
author: "Keeley MacAfee"
date: "2/25/2019"
output: html_document
citation_package: natbib
bibliography: bibliography.bib
---


# Abstract
In this commentary, I aim to expand upon Ryan Enos' article "Causal effect of intergroup contact on exclusionary attitudes." Using the data he collected, I examine the magnitude of the change in response to the three survey questions Enos asked regarding opinions on immigration. In this case, I chose to use the magnitude of change to eliminate the inconsistency in measuring the change in response on the 1-5 strongly agree to strongly disagree scale, as the meaning of positive or negative change in response varies between questions. Thus, by examining age, education, and income, I determine which of these factors, if any, affect respondents' malleability in either direction.

Good abstract

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ri)
library(RItools)
library(car)
library(xtable)
library(effects)
library(RColorBrewer)
library(gt)
library(kableExtra)
library(rstanarm)
library(tidyverse)
```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load data in. Only need full data set.

raw.data <- read_csv("dataverse_files/pnas_data.csv")

# I elected to use only magnitude of change because I found the connotations of the questions to be different. For example, the change in response to the third question has a different meaning than a change in response to the first two.
# I just want to look at how much attitudes changed in general rather than distinguishing between exclusionary vs softening attitudes as a result of exposure to outgroups. I felt that Enos on one hand made the claim that people became more exclusionary but on the other hand argued that prolonged exposure could also make people more accepting. 

# Nice commenting

# Might want to clarify and talk a little bit more about your choice to use magnitude of chance and
# what that means for the research overall

#This is data for all respondents. 
x <- raw.data %>%
select(X1, treated_unit, numberim.x, numberim.y, Remain.x, Remain.y, Englishlan.x, Englishlan.y, age, education, income, treatment) %>%
  # Here, I calculate the change in attitude by each question as well as calculate 
  # the aggregate change in responses to all questions.
  mutate(number.im.change = numberim.y - numberim.x,
         remain.change = Remain.y - Remain.x,
         english.change = Englishlan.y - Englishlan.x,
         q.full.x = numberim.x + Remain.x + Englishlan.x,
         q.full.y = numberim.y + Remain.y + Englishlan.y,
         q.full.change = q.full.y - q.full.x) %>%
  # To measure magnitude of change, I take the absolute value of the change in response for all questions. 
  mutate(mag.change = abs(q.full.change)) %>%
  filter(q.full.change != "NA")

#Control group
control <- x %>%
  filter(treatment == 0)

#Treated group
treated <- x %>%
  filter(treatment == 1)
```



#All Respondents Regressions
In these three regressions, I use age, education, and income separately to determine if they had an impact on the magnitude of change in attitude among all of the respondents (control group and treated group).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# All respondents: age/magnitude
# No significance 
# lm(mag.change ~ age, data = x) %>%
#   summary()

ggplot(x, aes(x = age, y = mag.change)) + geom_smooth(method = "lm") + xlab("Age") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Age: All Respondents")
```

In this case, age is insignificant (p = 0.56). 



```{r, echo=FALSE, message=FALSE, warning=FALSE}
# All respondents: education/magnitude
# lm(mag.change ~ education, data = x) %>%
#   summary()

ggplot(x, aes(x = education, y = mag.change)) + geom_smooth(method = "lm") + xlab("Education") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Education: All Respondents")
```

In this case, education is insignificant (p = 0.63).



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#All respondents: income/magnitude
# lm(mag.change ~ income, data = x) %>%
#   summary()

ggplot(x, aes(x = income, y = mag.change)) + geom_smooth(method = "lm") + xlab("Income") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Income: All Respondents")
```

In this case, income is insignificant (p = 0.51). 


#Control Group Regressions

In these three regressions, I use age, education, and income separately to determine if they had an impact on the magnitude of change in attitude among the control group. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Control: age/magnitude
# lm(mag.change ~ age, data = control) %>%
#   summary()

ggplot(treated, aes(x = age, y = mag.change)) + geom_smooth(method = "lm") + xlab("Age") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Age: Control")
```

In this case, age is insignificant (p = 0.70). 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Control: education
# lm(mag.change ~ education, data = control) %>%
#   summary()

ggplot(treated, aes(x = education, y = mag.change)) + geom_smooth(method = "lm") + xlab("Education") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Education: Control")
```

In this case, education is insignificant (p = 0.18). 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Control: income
# lm(mag.change ~ income, data = control) %>%
#   summary()

ggplot(treated, aes(x = income, y = mag.change)) + geom_smooth(method = "lm") + xlab("Income") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Income: Control")
```

In this case, income is insignificant (p = 0.08).

# Treated Group Regressions

In these three regressions, I use age, education, and income separately to determine if they had an impact on the magnitude of change in attitude among the treated group. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Treatment: age
# lm(mag.change ~ age, data = treated) %>%
#   summary()

ggplot(treated, aes(x = age, y = mag.change)) + geom_smooth(method = "lm") + xlab("Age") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Age: Treatment")
```

In this case, age is insignificant (p = 0.56).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Treatment: education
# lm(mag.change ~ education, data = treated) %>%
#   summary()

ggplot(treated, aes(x = education, y = mag.change)) + geom_smooth(method = "lm") + xlab("Education") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Education: Treatment")
```

In this case, education is insignificant (p = 0.60).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Treatment: income
# lm(mag.change ~ income, data = treated) %>%
#   summary()

ggplot(treated, aes(x = income, y = mag.change)) + geom_smooth(method = "lm") + xlab("Income") + ylab("Magnitude of Change") + ggtitle("Magnitude of Change by Income: Treatment")
```

In this case, income is insignificant (p = 0.38).

# Bonus Regression 



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Income: q full (KEEP AS BONUS...SIGNIFICANT)
# lm(q.full.change ~ income, data = x) %>%
#   summary()

ggplot(x, aes(x = income, y = q.full.change)) + geom_smooth(method = "lm") + xlab("Income") + ylab("Change") + ggtitle("Raw Change by Income: All Respondents")

# After the magnitude by each factor was insignificant, I wanted to determine 
# if using the direction of attitudes made a difference. To my surprise, income 
# was the only factor with statistical significance. 

# Good looking plot for the regressions, it would be useful for the reader is they contained a bit more
# information like what type of regression is being used and any other useful info in a footnote so there
# is no guessing
```

In this case, the intercept has a significant p value (0.01), and income is also significant (p =0.008). This regression shows that changes in income are related to changes in the direction, but not necessarily to the magnitude, of attitude shifts among respondents. 

# Conclusion
My hypothesis that age, education, and income would impact the magnitude of respondents' change in attitude proved to have no statistical support. I originally believed that these factors, age especially, would affect respondents' responses to the treatment, with younger people being more impressionable in either direction. While age and magnitude have a slight negative correlation in all respondents, the control group, and the treatment group, there is still high variance in each case.  

Excellent idea to include a conclusion summarizing hypotheses and results!

# References
```{r, echo =FALSE, message=FALSE}
# I am not sure why, but the references from the bibliography.bib file do not show up. I copied Preceptor's bibliography and his title format at the beginning of the rmd. 
```

